% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009

\documentclass{acm_proc_article-sp}

\usepackage{todonotes}
\usepackage{algorithm}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage{mdframed}
\usepackage{amsmath}

\newtheorem{defn}{\textbf{Definition}}
\newtheorem{thm}{\textbf{Theorem}}
\newtheorem{cor}{\textbf{Corollary}}
\newtheorem{lemma}{\textbf{Lemma}}

\begin{document}

\title{AND: High Performance Anonymous Named Data}

\numberofauthors{3} 
\author{
% 1st. author
\alignauthor
Christopher A. Wood\titlenote{NSF GRFP blurb.}\\
       \affaddr{University of California Irvine}\\
       \affaddr{Irvine, CA, USA}\\
       \email{woodc1@uci.edu}
% 2nd. author
\alignauthor
Gene Tsudik\\
       \affaddr{University of California Irvine}\\
       \affaddr{Irvine, CA, USA}\\
       \email{gts@ics.uci.edu}
% 3rd. author
\alignauthor 
Ersin Uzun\\
       \affaddr{PARC}\\
       \affaddr{Palo Alto, CA, USA}\\
       \email{Ersin.Uzun@parm.com}
}
\date{\today}

\maketitle
\begin{abstract}
With the increasing trend of personal and private activities and correspondence conducted on the Internet, the need for anonymous communication provided by services such as Tor continues to escalate. Furthermore, as information-centric networking (ICN) gains momentum, the need for a Tor-like analog to support high performance anonymous communication rises at an equal rate. ICN designs such as Named Data Networking are unique in that all communication is content-based rather than host-based, i.e., content, rather than hosts, are addressable in the network. In order to mask user locations and identities, it becomes necessary to mask the process in which content is requested. {\sf ANDaNA} (Anonymous Named Data Networking Application) was the first attempt to provide this type of anonymity in the context of NDN. However, its elementary design and implementation led to severe performance issues that would hinder widespread usage. To this end, we propose {\sf AND}, a new and vastly improved variant of {\sf ANDaNA}, to support high throughput and low latency anonymous content retrieval in NDN in unidirectional and bidirectional settings. In this work, we describe the design, implementation, and performance of {\sf AND}, and also prove various anonymity guarantees provided by our design. Our experimental results show that {\sf AND} introduces minimal overhead with a minimal number of anonymizing proxies (1), while simultaneously ensuring anonymity guarantees similar to Tor.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{TODO}{TODO}
%A category including the fourth, optional field follows...
\category{D.2.8}{TODO}{TODO}[TODO]

\terms{NDN, Anonymity, Tor}

% \keywords{TODO} % NOT required for Proceedings

\input{01-intro}
\input{02-prelims}
\input{03-design}
\input{04-implementation}
\input{06-security}
\input{05-performance}

% \section{Conclusion}
% TODO

% \section{Acknowledgments}
% TODO

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{ref}  % sigproc.bib is the name of the Bibliography in this case

% \appendix
% %Appendix A
% \section{Headings in Appendices}
% The rules about hierarchical headings discussed above for
% the body of the article are different in the appendices.
% In the \textbf{appendix} environment, the command
% \textbf{section} is used to
% indicate the start of each Appendix, with alphabetic order
% designation (i.e. the first is A, the second B, etc.) and
% a title (if you include one).  So, if you need
% hierarchical structure
% \textit{within} an Appendix, start with \textbf{subsection} as the
% highest level. Here is an outline of the body of this
% document in Appendix-appropriate form:
% \subsection{Introduction}
% \subsection{The Body of the Paper}
% \subsubsection{Type Changes and  Special Characters}
% \subsubsection{Math Equations}
% \paragraph{Inline (In-text) Equations}
% \paragraph{Display Equations}
% \subsubsection{Citations}
% \subsubsection{Tables}
% \subsubsection{Figures}
% \subsubsection{Theorem-like Constructs}
% \subsubsection*{A Caveat for the \TeX\ Expert}
% \subsection{Conclusions}
% \subsection{Acknowledgments}
% \subsection{Additional Authors}
% This section is inserted by \LaTeX; you do not insert it.
% You just add the names and information in the
% \texttt{{\char'134}additionalauthors} command at the start
% of the document.
% \subsection{References}
% Generated by bibtex from your ~.bib file.  Run latex,
% then bibtex, then latex twice (to resolve references)
% to create the ~.bbl file.  Insert that ~.bbl file into
% the .tex source file and comment out
% the command \texttt{{\char'134}thebibliography}.
% % This next section command marks the start of
% % Appendix B, and does not continue the present hierarchy
% \section{More Help for the Hardy}
% The acm\_proc\_article-sp document class file itself is chock-full of succinct
% and helpful comments.  If you consider yourself a moderately
% experienced to expert user of \LaTeX, you may find reading
% it useful but please remember not to change it.
% \balancecolumns
% % That's all folks!

\end{document}
